\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-11 syntax.tex
Save. Rephrasing.

Of course, any fields using "Wsup" and "Wrec" directly relies on the $\bW(\sigma)$ and thus non-inheritable -- in these cases, "Wsup" can be understood as concrete constructors and "Wrec" are \textit{exhaustiveness checking}. These fields together with inductive types are the one sealing responsible for hiding. After compilation of linkage type into existential type, we can easily hide the textit{concrete} definition of the inductive type while exposing all the fields using "Wsup" and "Wrec" like an abstract interface. Apparently, future fields relies on this abstract interface will have no problem on inheritance. \YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear -- because I haven't changed any text}

@@

However, there are cases we don't need to seal anything (i.e. doing exhaustiveness checking when using recursor), and thus the "Seal-Id" is used. For notation clearance, we will sometime use $sf'$ to emphasize that we consider that seal $s$ as a term $(sf' \ s)$.

Note that, there will be a lot of $\sigma_1, \sigma_1'$ and $\sigma_2, \sigma_2'$, in these cases, $\sigma_1'$ is the result of the sealing of $\sigma_1$, i.e. we assume we have a term $\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}, \goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the assumption when needed.

>>>>

Of course, any fields using "Wsup" and "Wrec" directly relies on the $\bW(\sigma)$ and thus non-inheritable -- in these cases, "Wsup" can be understood as concrete constructors and "Wrec" are \textit{exhaustiveness checking}. These fields together with inductive types are the one sealing responsible for hiding. After compilation of linkage type into existential type, we can easily hide the \textit{concrete} definition of the inductive type while exposing all the fields using "Wsup" and "Wrec" like an abstract interface. Apparently, future fields relies on this abstract interface will have no problem on inheritance. \YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear -- because I haven't changed any text}

@@

And these are also the cases we don't need to seal anything (i.e. doing exhaustiveness checking when using recursor), and thus the "Seal-Id" is used. For notation clearance, we will sometime use $sf'$ to emphasize that we consider that seal $s$ as a term $(sf' \ s)$.

Note that, there will be a lot of $\sigma_1, A_1$ and $\sigma_2, A_2$, in these cases, $A_1$ is the result of the sealing of $\sigma_1$, i.e. we assume we have a term $\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}, \goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the assumption when needed.
